### 2015-11-05 paper.Rmd
add pdf

  curve(gmix, from=0, to=1, xlab="", ylab="",
        main=bquote(sigma[1] == .(sig1) ~ sigma[2] == .(sig2) ~  phi[1] == .(mix)),
        xlim=c(0,1), ylim=c(0,1), asp=1)
  title(xlab="Distance", line=2)
  title(ylab="Detection probability", line=2)
}
plotmix(0.8, 0.15, 0.3)
plotmix(0.6, 0.1,0.7)
plotmix(10, 0.2, 0.15)
plotmix(0.7, 0.05, 0.6)

@@

When multiple covariates are used in the model, a series of plots are produced. We can see this in the bottom row of **Figure ???**, where we plot the results of fitting following model:
```{r amakihi-hr-obs-mas}
amakihi_hr_obs_mas <- ds(amakihi, truncation=82.5, transect="point",
                         model=df(model=~hr, scale=~obs+mas))
```

```{r minke-hn-plot, fig.width=9, fig.height=9, fig.cap="Plot of fitted detection functions overlayed on the histograms of observed distances. Top row the minke whale data, half-normal model. Bottom row: average detection function for the amakihi data and marginal plot showing the levels of observer."}
par(mfrow=c(3,3))
plot(minke_hn, nomf=TRUE)
plot(1:10,1:10, main="",xlab="",ylab="",type="n", axes=FALSE)
plot(1:10,1:10, main="",xlab="",ylab="",type="n", axes=FALSE)
plot(amakihi_hr_obs, nomf=TRUE)
plot(1:10,1:10, main="",xlab="",ylab="",type="n", axes=FALSE)
plot(amakihi_hr_obs_mas, nomf=TRUE)
```

>>>>

  curve(gmix, from=0, to=1, xlab="", ylab="",
        main=bquote(sigma[1] == .(sig1) ~ sigma[2] == .(sig2) ~  phi[1] == .(mix)),
        xlim=c(0,1), ylim=c(0,1), asp=1)
  title(xlab="Distance", line=2)
  title(ylab="Detection probability", line=2)
}
plotmix(0.8, 0.15, 0.3)
plotmix(0.6, 0.1,0.7)
plotmix(10, 0.2, 0.15)
plotmix(0.7, 0.05, 0.6)
```

@@

When multiple covariates are used in the model, a series of plots are produced. We can see this in the bottom row of **Figure ???**, where we plot the results of fitting following model:
```{r amakihi-hr-obs-mas, warning=FALSE}
amakihi_hr_obs_mas <- ds(amakihi, truncation=82.5, transect="point",
                         model=df(model=~hr, scale=~obs+mas))
```

```{r minke-hn-plot, echo=FALSE, warning=FALSE, fig.width=9, fig.height=9, fig.cap="Plot of fitted detection functions overlayed on the histograms of observed distances. Top row the minke whale data, half-normal model. Bottom row: average detection function for the amakihi data and marginal plot showing the levels of observer."}
par(mfrow=c(3,3))
plot(minke_hn, nomf=TRUE)
plot(1:10,1:10, main="",xlab="",ylab="",type="n", axes=FALSE)
plot(1:10,1:10, main="",xlab="",ylab="",type="n", axes=FALSE)
plot(amakihi_hr_obs, nomf=TRUE)
plot(1:10,1:10, main="",xlab="",ylab="",type="n", axes=FALSE)
plot(amakihi_hr_obs_mas, nomf=TRUE)
```
